---
title       : Vehicle Fuel Economy Analysis 
subtitle    : Interactive analysis of Vehicle Fuel Economy
author      : Mala
job         : IT Consultant
framework   : io2012          # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js    # {highlight.js, prettify, highlight}
hitheme     : solarized_light # tomorrow 
widgets     : [polycharts, bootstrap, shiny, interactive]
mode        : selfcontained   # {standalone, selfcontained,draft}
ext_widgets : {rCharts: [libraries/nvd3]}
knit        : slidify::knit2slides
---

### Vehicle Fuel Economy Analysis
Vehicle Fuel Economy Analysis applicationapp provides an interactive analysis of vehicles fuel combined consumption (city and highway) and annual fuel cost is based on 15,000 miles, 55% city driving, and the price of fuel used by the vehicle based on year make,model and Transmission type(Automatic/Manual).

The raw data for this analysis is downloaded from U.S Department of Energy (Office Of Transportation & Air Quality) http://www.fueleconomy.gov/

The data is spanned from year 1984 to 2015.Only subset of data is used in this application.

### Vehicle Fuel Economy Analysis Plots 
In Vehicle Fuel Economy Analysis, the following analaysis are done for different car models (Audi,BMW...) considering their transmission type, also the fuel types they use.
- Vehicle you (+)Spend/(-)Save (Shown in this slidify)
- Miles Per Gallons(City & Highway) 
- Fuel Economy Score by Fuel Type and Make (Shown in this slidify)
- Annual petroleum consumption in barrels

---


```{r, echo = FALSE, cache = TRUE}


#Read Data for You Spend Save data
vehicleSumData<-read.csv("VchSumData.csv")
#Read Data for Fe Score 
vehicleFeScore<-read.csv("VchfeScore.csv")

suppressMessages(library(rCharts))
suppressMessages(library(slidify))




```

## Interactive Vehicle (+)Spend/(-)Save per year

```{r echo = F, results = 'asis'}

stkPlot<-nPlot(youSaveSpend ~ year, group = 'transtype', 
                 data = vehicleSumData, 
                 type = 'multiBarChart', dom = 'stkchart', width = 600) 

        stkPlot$yAxis(tickFormat = "#! function(d) {return '' + d3.format(',.')(d)} !#")
        stkPlot$chart(margin = list(left = 100))
        stkPlot$yAxis( axisLabel = "Vehicle (+)Spend/(-)Save", width = 80)
        
stkPlot$print('stkchart')
```

---

## Interactive Fuel Economy Score by Fuel Type by year for Automatic

```{r echo = F, results = 'asis'}
AutovehFeScore<-subset(vehicleFeScore,transtype=='Automatic')

sccplot1 <- nPlot(feScore ~ year, group = 'atvType', data = AutovehFeScore, 
                  type='scatterChart', dom = 'sctchart1', width = 600)


sccplot1$yAxis(axisLabel = "Fuel Economy Score Automatic", tickFormat = "#! function(d) {return '' + d} !#")
sccplot1$xAxis( axisLabel = "Year")
sccplot1$chart(size = '#! function(d){return d.feScore} !#')
sccplot1$yAxis(tickFormat = "#! function(d) {return '' + d3.format(',.')(d)} !#")
sccplot1$chart(margin = list(right = 100))
sccplot1$print('sctchart1')
```

---

## Interactive Fuel Economy Score by Fuel Type by year for Manual

```{r echo = F, results = 'asis'}
ManvehFeScore<-subset(vehicleFeScore,transtype=='Manual')



sccplot2 <- nPlot(feScore ~ year, group = 'atvType', data = ManvehFeScore, 
                  type='scatterChart', dom = 'sctchart2', width = 600)

sccplot2$yAxis(axisLabel = "Fuel Economy Score Automatic", tickFormat = "#! function(d) {return '' + d} !#")
sccplot2$xAxis( axisLabel = "Year")
sccplot2$chart(size = '#! function(d){return d.feScore} !#')
sccplot2$yAxis(tickFormat = "#! function(d) {return '' + d3.format(',.')(d)} !#")
sccplot2$chart(margin = list(right = 100))
sccplot2$print('sctchart2')
```
